Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline.

### 2017-04-25 draft/ms_v4.tex
cModel color

    In Fig \ref{fig:cmodel_color}, we demonstrate the accuracies of \forced{} $(g-i)$
    and $(i-y)$ \cmodel{} colors in the same format used for synthetic stars
    (Fig \ref{fig:psf_color}).
    These plots show that \hscpipe{} can provide reliable \cmodel{} colors for
    synthetic galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
    For $(g-i)$ colors, the average uncertainty around $i_{\mathrm{Input}}{\sim}21.0$ mag
    is ${\sim}0.04$ mag.
    The uncertainty increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}25.0$ mag.
    Results for $(i-y)$ colors are similar.

    The performance of \forced{} \cmodel{} color does not show dependence on seeing
    condition, and it is unbiased across the ranges for input total magnitude and color.
    The only noticeable feature is that the $(i-y)$ color at
    $i_{\mathrm{Input}}>24.0$ is slightly overestimated.
    As mentioned above, this is not surprising given the shallower imaging depth of  the
    $y$-band.
    At the same time, high blendedness of synthetic galaxies can still increase the
   color uncertainties and bias the color measurements.
    The highly blended galaxies on average show slightly bluer  $(g-i)$ colors
     and redder  $(i-y)$ colors  than the input values.

    Similar to the star comparison in Fig \ref{fig:psf_cdist}, we also compare the color--color distributions
    of the input and output \forced{} \cmodel{} values in Fig \ref{fig:cmodel_cdist}.
    The general color distributions are well recovered despite the fact that the galaxy accuracy is
    not as good as the accuracy for stars, especially on the $(i-z)$ vs. $(z-y)$ plane.
    That result is expected given the narrow dynamical ranges of these colors among red filters.
    The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
    colors at the very ``blue'' end, while overestimating the $(i-y)$ color at the very
    red end.

   We should point out that we assume constant color for the entire galaxy.
    In reality, different colors for individual components and a smooth color gradient
    can complicate the situation; hence, the uncertainties of \cmodel{} colors
    here should be considered as lower limits.
%% ------------------------------------------------------------------------------------ %%

>>>>

    In Fig \ref{fig:cmodel_color}, we demonstrate the accuracies of \forced{} $(g-i)$
    and $(i-y)$ \cmodel{} colors in the same format for synthetic stars
    (Fig \ref{fig:psf_color}).
    They confirm that \hscpipe{} can provide reliable \cmodel{} colors for synthetic 
    galaxies down to $i_{\mathrm{Input}}{\sim}25.0$ mag.
    For $(g-i)$ colors, the average uncertainty at $i_{\mathrm{Input}}{\sim}21.0$ mag
    is ${\sim}0.04$ mag.
    The uncertainty increases to ${\sim}0.11$ mag at $i_{\mathrm{Input}}{\sim}25.0$ mag.
    $(i-y)$ colors show similar results.

    The performance of \forced{} \cmodel{} color does not depend on seeing and is 
    unbiased for entire ranges of input magnitudes and colors.
    The only noticeable feature is that the $(i-y)$ color at $i_{\mathrm{Input}}>24.0$ 
    is slightly overestimated.
    As mentioned above, this is not surprising given the shallower imaging depth in
    $y$ band.
    Meanwhile, high blendedness also increases the color uncertainties and biases the 
    color measurements.
    The highly blended galaxies on average show slightly bluer $(g-i)$ colors and redder  
    $(i-y)$ colors than the input ones.

    Similar to Fig \ref{fig:psf_cdist}, we also compare the color--color distributions
    of the input and output \forced{} \cmodel{} values in Fig \ref{fig:cmodel_cdist}.
    The general 2--D distributions are well recovered but the accuracy is not as good as 
    the one for stars, especially on the $(i-z)$ vs. $(z-y)$ plane.
    This is expected given the narrow dynamical ranges of these colors among red filters.
    The \forced{} \cmodel{} tends to slightly underestimate the $(g-r)$ and $(i-z)$
    colors at the very ``blue'' end, while overestimating the $(i-y)$ color at the very
    red end.

    We should point out that we assume constant color for the entire galaxy.
    In reality, different colors for individual component or color gradient can 
    complicate the situation.
    The uncertainties of \cmodel{} colors here should be considered as lower limits.
%% ------------------------------------------------------------------------------------ %%
